\textbf{\huge EHDA closed loop control system based on real time non-visual spray mode classification}\\ (Center, Bold, Times New Roman 14, maximum 15 words in english)

### 2023-02-02 Documentation/WT group/article1/main.tex
new abstract

\noindent\rule{15cm}{0.5pt}
	\begin{abstract}
		This article presents a closed-loop control system for EHDA (Electrohydrodynamic Atomization) that utilizes real-time, non-visual spray mode classification to improve performance, accuracy and efficiency in both research and industries applications.
		EHDA is a method of atomizing liquids using an electric field, which can generate droplets smaller than the nozzle diameter with a controlled droplet size.
		The system uses current data to classify the spray mode dynamics in real-time and adjust EHDA parameters such as pump flowrate and power supply voltage to reach the desired spray mode and stabilize it.
		The proposed control algorithm is able to achieve improved accuracy and reduced waste compared to previous manual methods.
		The potential applications of the system are discussed, including in industrial processes such as spray coating and gas odorizing.

@@

		}
		\textbf{\textit{Keywords}}: \textit{Electrospray; EHDA Control System; EHDA Automation; keyword 4; keyword 5}
	\end{abstract}
\noindent\rule{15cm}{0.4pt}

>>>>

\noindent\rule{15cm}{0.5pt}
	\begin{abstract}

			We present a closed-loop control system for Electrohydrodynamic Atomization (EHDA) systems that utilizes real-time, non-visual spray mode classification to improve performance, accuracy and efficiency in both research and industrial applications.
		EHDA is a liquid atomization technique which, by using a high electric field, tiny charged droplets, much smaller than the nozzle diameter, can be generated with a controlled droplet size. 
		The system uses real-time acquired data to classify the spray mode dynamics and adjusts EHDA operation parameters such as liquid flowrate and applied voltage to reach the desired spray mode maintain it stable. 
		The proposed control algorithm is able to achieve improved accuracy and reduced waste compared to previous manual methods. 
		The potential applications of the system are discussed, including industrial processes such as spray coating and gas odorization.

@@

		}
		\textbf{\textit{Keywords}}: \textit{Electrospray; EHDA Control System; EHDA Automation; Electrospray mode classification}
	\end{abstract}
\noindent\rule{15cm}{0.4pt}
